### 2022-03-30 paper/localpsf.tex
editing intro

\section{Setting}

Let $\Omega \subset \mathbb{R}^d$ be a bounded domain (in applications typically $\gdim=1$, $2$, or $3$). We seek to approximate integral operators $\Aop:L^2(\Omega)\rightarrow L^2(\Omega)'$ that may be written in the following form:
\begin{equation}
	\label{eq:kernel_representation}
	(\Aop u)(v) := \int_\Omega \int_\Omega v(y) \Aker(y,x) u(x) dx dy.
\end{equation}
The function $\Aker:\Omega \times \Omega \rightarrow \mathbb{R}$ is the integral kernel, which exists in principle but is not easily accessible to us. 
%We write $L^2(\Omega)'$ to denote the topological dual of $L^2(\Omega)$. 
%The linear functional $\Aop u \in L^2(\Omega)'$ is the result of applying $\Aop$ to $u\in L^2(\Omega)$, and $\left(\Aop u\right)(v)$ is the scalar that results from applying that linear functional to $v \in L^2(\Omega)$.

@@

In this paper, we focus on approximating operators that satisfy the following conditions: 
\begin{enumerate}
	\item The kernel $\Phi$ is sufficiently regular such that $\phi_x$ is a well-defined function for all $x\in \Omega$.
	\item The supports of the impulse responses $\impulseresponse_x$ are contained in localized regions.
	\item The integral kernel is non-negative in the sense that $$\Phi(y,x) \ge 0$$ for all $(y,x) \in \Omega \times \Omega$.\footnote{Note that having a non-negative integral kernel is different from positive semi-definiteness. The operator $\Aop$ need not be positive semi-definite to use our method, and positive semi-definite operators need not have a non-negative integral kernel.}
\end{enumerate}
Our method may still perform well if these conditions are relaxed slightly. For example, it is fine if the support of the impulse response $\impulseresponse_x$ is not perfectly contained in a localized region, so long as the bulk of the ``mass'' of the impulse response is contained in a localized region. The integral kernel does not need to be non-negative for all pairs of points $(y,x) \in \Omega \times \Omega$, as long as it is non-negative for the vast majority of pairs of points $(y,x)$, and as long as the negative numbers are comparatively small. If these conditions are violated, our method will incur additional error. If these conditions are violated too much, our method may fail. Not all operators of interest (and in particular not all Hessians) satisfy these conditions, but many operators of practical interest do satisfy these conditions, and our method is highly effective for approximating these operators.
%Because of these conditions, we are able to estimate the supports of the impulse responses a-priori by applying $\Aop^T$ \footnote{Recall that the transpose of $\Aop:L^2(\Omega)\rightarrow L^2(\Omega)'$ is the unique operator $\Aop^T:L^2(\Omega)\rightarrow L^2(\Omega)'$ satisfying $\left(\Aop u\right)(v) = \left(\Aop^T v\right)(u)$ for all $u,v\in L^2(\Omega)$.} to a small number of polynomial functions (Section \ref{sec:intromoments}). We use the support estimates to compute scattered impulse responses in batches (Section \ref{sec:get_impulse_response}, also Figure \ref{fig:batches_intro}). This batching allows us to recover many impulse responses using a small number of operator actions $u \mapsto \Aop u$. The support estimates also allow us to interpolate the impulse responses with a new more sophisticated and accurate interpolation scheme (Sections \ref{sec:local_mean_displacement_invariance} and \ref{sec:approximate_kernel_entries}).

@@

\subsubsection{Lumped mass matrix and discrete kernel non-negativity}

>>>>

\section{Preliminaries}

Let $\Omega \subset \mathbb{R}^d$ be a bounded domain (in applications typically $\gdim=1$, $2$, or $3$). We seek to approximate integral operators $\Aop:L^2(\Omega)\rightarrow L^2(\Omega)'$ that may be written in the following form:
\begin{equation}
\label{eq:kernel_representation}
(\Aop u)(v) := \int_\Omega \int_\Omega v(y) \Aker(y,x) u(x) dx dy.
\end{equation}
The function $\Aker:\Omega \times \Omega \rightarrow \mathbb{R}$ is the integral kernel, which exists in principle but is not easily accessible to us. In this section we describe how to extend the action of $\Aop$ to distributions , and define impulse responses (Section \ref{sec:impulse_response_2}). Then we state the conditions on $\Aop$ that our method requires (Section \ref{sec:conditions_2}). Finally, we detail finite element discretization (Section \ref{sec:finite_element_kernel}).
%We write $L^2(\Omega)'$ to denote the topological dual of $L^2(\Omega)$. 
%The linear functional $\Aop u \in L^2(\Omega)'$ is the result of applying $\Aop$ to $u\in L^2(\Omega)$, and $\left(\Aop u\right)(v)$ is the scalar that results from applying that linear functional to $v \in L^2(\Omega)$.

\subsection{Action on distributions and impulse responses}
\label{sec:impulse_response_2}

@@

\subsection{Required conditions}
\label{sec:conditions_2}

We focus on approximating operators that satisfy the following conditions: 
\begin{enumerate}
	\item The kernel $\Phi$ is sufficiently regular such that $\phi_x$ is a well-defined function for all $x\in \Omega$.
	\item The supports of the impulse responses $\impulseresponse_x$ are contained in localized regions.
	\item The integral kernel is non-negative in the sense that $$\Phi(y,x) \ge 0$$ for all $(y,x) \in \Omega \times \Omega$.\footnote{Note that having a non-negative integral kernel is different from positive semi-definiteness. The operator $\Aop$ need not be positive semi-definite to use our method, and positive semi-definite operators need not have a non-negative integral kernel.}
\end{enumerate}
Our method may still perform well if these conditions are relaxed slightly. For example, it is fine if the support of the impulse response $\impulseresponse_x$ is not perfectly contained in a localized region, so long as the bulk of the ``mass'' of the impulse response is contained in a localized region. The integral kernel does not need to be non-negative for all pairs of points $(y,x) \in \Omega \times \Omega$, as long as it is non-negative for the vast majority of pairs of points $(y,x)$, and as long as the negative numbers are comparatively small. If these conditions are violated, our method will incur additional error. If these conditions are violated too much, our method may fail. Not all operators of interest (and in particular not all Hessians) satisfy these conditions, but many operators of practical interest do satisfy these conditions, and our method is highly effective for approximating these operators.
%Because of these conditions, we are able to estimate the supports of the impulse responses a-priori by applying $\Aop^T$ \footnote{Recall that the transpose of $\Aop:L^2(\Omega)\rightarrow L^2(\Omega)'$ is the unique operator $\Aop^T:L^2(\Omega)\rightarrow L^2(\Omega)'$ satisfying $\left(\Aop u\right)(v) = \left(\Aop^T v\right)(u)$ for all $u,v\in L^2(\Omega)$.} to a small number of polynomial functions (Section \ref{sec:intromoments}). We use the support estimates to compute scattered impulse responses in batches (Section \ref{sec:get_impulse_response}, also Figure \ref{fig:batches_intro}). This batching allows us to recover many impulse responses using a small number of operator actions $u \mapsto \Aop u$. The support estimates also allow us to interpolate the impulse responses with a new more sophisticated and accurate interpolation scheme (Sections \ref{sec:local_mean_displacement_invariance} and \ref{sec:approximate_kernel_entries}).

@@

%\subsubsection{Lumped mass matrix and discrete kernel non-negativity}
